Data Analysis Methods for the Detection of the Epoch of Reionization

### 2017-11-22 PAPER.tex
minor text changes

\begin{figure*}
	\centering
	\includegraphics[width=0.4\textwidth]{plots/ps2_data_nosigloss.png}
	\includegraphics[width=0.4\textwidth]{plots/ps2_data.png}
	\caption{Full inverse covariance weighted power spectrum of PAPER-64 data (positive (black) and negative (grey) points, 
with $2\sigma$ error bars) before signal loss correction (left) and after (right). The dashed blue line is the unweighted power 
spectrum ($2\sigma$ upper limit). The solid green line is the theoretical noise level prediction based on observational 
parameters, whose calculation is detailed in Section \ref{sec:PSSense}.}
	\label{fig:ps2_data}
\end{figure*}

@@

\begin{figure*}
	\centering
	\includegraphics[width=0.4\textwidth]{plots/ps1_data_reg.png}
	\includegraphics[width=0.4\textwidth]{plots/ps2_data_reg.png}
	\caption{Power spectrum of PAPER-64 using $\hat{\textbf{C}}_{eff}$. Black and grey points correspond to positive and 
negative power spectrum values, respectively, with $2\sigma$ error bars also plotted. The dashed blue line is the unweighted 
power spectrum ($2\sigma$ upper limit). The solid green line is the theoretical noise level prediction based on observational 
parameters. This power spectrum result differs from P64 in that it only uses data from one type of baseline ($30$ m East/West 
baselines) instead of three. Major differences from previously published results stem from revisions regarding signal loss, 
bootstrapping, and the theoretical error computation. We quote a best $2\sigma$ upper limit of $(158.0$ mK$)^{2}$ at $k=0.34$ 
$h$Mpc$^{-1}$, a higher limit than P64 by a factor of $\sim7$ in mK \cc{ref kolopanis limit instead later}.}
	\label{fig:ps1_data}
\end{figure*}

@@

\begin{figure*}
	\centering
	\includegraphics[width=0.4\textwidth]{plots/ps1_noise_reg.png}
	\includegraphics[width=0.4\textwidth]{plots/ps2_noise_reg.png}
	\caption{Power spectrum estimate for a noise simulation that mimics the noise level of PAPER-64 data. The weighted 
power spectrum points and $2\sigma$ errors are show in black and grey (positive and negative values), where we use $
\hat{\textbf{C}}_{eff}$ to minimize signal loss. The dashed blue line is the unweighted power spectrum (also $2\sigma$ upper 
limit). The solid green line is the theoretical noise level prediction as calculated by Equation \eqref{eq:sense}. All three 
estimates agree.}
	\label{fig:ps_noise}
\end{figure*}

@@

\begin{figure}
	\centering
	\includegraphics[trim={0.3cm 0.3cm 0.3cm 0.3cm},width=\columnwidth]{plots/data_errors.png}
	\caption{$2\sigma$ power spectrum errors (not upper limits) using PAPER-64 data and three different bootstrapping 
methods. The data is fringe-rate filtered and a weighting matrix of $\textbf{I}$ (unweighted) is used in order to disentangle the 
effects of bootstrapping from signal loss. Three different bootstrapping methods are shown: the blue and black use methods 
where bootstrapping occurs on the baseline axis only (not the time axis), and they differ by how the baselines are randomly 
sampled. It is evident that sensitivity is maximized when baselines are sampled in a way that ensures mostly independent 
samples (only the last baseline spot is sampled randomly), as shown by the black curve. In red, bootstrapping occurs over both 
the baseline and time axes, illustrating how errors can be under-estimated if sampling more values than independent ones 
(fringe-rate filtering reduces the number of independent samples). We use the method illustrated by the black curve in our 
updated analysis, which is shown to agree with the analytic prediction for noise (green).}
	\label{fig:data_errors}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{plots/null.png}
	\caption{Results for $3$ null tests compared to the PAPER-64 revised power spectrum (black) and estimated $2\sigma$ 
errors (grey shaded region). For each, we took jackknives along different axes of the dataset - by julian days (separating even 
and odd days; blue), by baselines (green), and by LST (purple). We expect the sky signal to disappear for a `passing' null test. 
We find that the biases in our power spectrum are likely caused by variation of foregrounds in LST, and are not attributable to 
particular baselines or days of data.}
	\label{fig:null}
\end{figure}

>>>>

\begin{figure*}
	\centering
	\includegraphics[width=0.4\textwidth]{plots/ps2_data_nosigloss.png}
	\includegraphics[width=0.4\textwidth]{plots/ps2_data.png}
	\caption{Full inverse covariance weighted power spectrum of PAPER-64 data (positive (black) and negative (grey) points, 
with $2\sigma$ error bars) before signal loss correction (left) and after (right). The dashed blue line is the unweighted power 
spectrum ($2\sigma$ upper limit). The solid green line is the theoretical $2\sigma$ noise level prediction based on observational 
parameters, whose calculation is detailed in Section \ref{sec:PSSense}.}
	\label{fig:ps2_data}
\end{figure*}

@@

\begin{figure*}
	\centering
	\includegraphics[width=0.4\textwidth]{plots/ps1_data_reg.png}
	\includegraphics[width=0.4\textwidth]{plots/ps2_data_reg.png}
	\caption{Power spectrum of PAPER-64 using $\hat{\textbf{C}}_{eff}$. Black and grey points correspond to positive and 
negative power spectrum values, respectively, with $2\sigma$ error bars also plotted. The dashed blue line is the unweighted 
power spectrum ($2\sigma$ upper limit). The solid green line is the theoretical $2\sigma$ noise level prediction based on 
observational parameters. This power spectrum result differs from P64 in that it only uses data from one type of baseline ($30$ m 
East/West baselines) instead of three. Major differences from previously published results stem from revisions regarding signal 
loss, bootstrapping, and the theoretical error computation. We quote a best $2\sigma$ upper limit of $(158.0$ mK$)^{2}$ at 
$k=0.34$ $h$Mpc$^{-1}$, a higher limit than P64 by a factor of $\sim7$ in mK \cc{ref kolopanis limit instead later}.}
	\label{fig:ps1_data}
\end{figure*}

@@

\begin{figure*}
	\centering
	\includegraphics[width=0.4\textwidth]{plots/ps1_noise_reg.png}
	\includegraphics[width=0.4\textwidth]{plots/ps2_noise_reg.png}
	\caption{Power spectrum estimate for a noise simulation that mimics the noise level of PAPER-64 data. The weighted 
power spectrum points and their $2\sigma$ errors are show in black and grey (positive and negative values), where we use $
\hat{\textbf{C}}_{eff}$ to minimize signal loss. The dashed blue line is the unweighted power spectrum (also $2\sigma$ upper 
limit). The solid green line is the theoretical $2\sigma$ noise level prediction as calculated by Equation \eqref{eq:sense}. All three 
estimates agree (the analytic curve should encompass $95\%$ of the points).}
	\label{fig:ps_noise}
\end{figure*}

@@

\begin{figure}
	\centering
	\includegraphics[trim={0.3cm 0.3cm 0.3cm 0.3cm},width=\columnwidth]{plots/data_errors.png}
	\caption{$2\sigma$ power spectrum errors (not upper limits) using PAPER-64 data and three different bootstrapping 
methods. The data is fringe-rate filtered and a weighting matrix of $\textbf{I}$ (unweighted) is used in order to disentangle the 
effects of bootstrapping from signal loss. Three different bootstrapping methods are shown: the blue and black use methods 
where bootstrapping occurs on the baseline axis only (not the time axis), and they differ by how the baselines are randomly 
sampled. It is evident that sensitivity is maximized when baselines are sampled in a way that ensures mostly independent 
samples (only the last baseline spot is sampled randomly), as shown by the black curve. In red, bootstrapping occurs over both 
the baseline and time axes, illustrating how errors can be under-estimated if sampling more values than independent ones 
(fringe-rate filtering reduces the number of independent samples). We use the method illustrated by the black curve in our 
updated analysis, which is shown to agree with the $2\sigma$ analytic prediction for noise (green).}
	\label{fig:data_errors}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{plots/null.png}
	\caption{Results for $3$ null tests compared to the PAPER-64 revised power spectrum (black) and analytically estimated 
$2\sigma$ errors (grey shaded region). For each, we took jackknives along different axes of the dataset - by julian days (separating 
even and odd days; blue), by baselines (green), and by LST (purple). We expect the sky signal to disappear for a `passing' null test. 
We find that the biases in our power spectrum are likely caused by variation of foregrounds in LST, and are not attributable to 
particular baselines or days of data.}
	\label{fig:null}
\end{figure}
